### 2022-10-14 README.Rmd
update readme, still need to do the example

@@

>>>>

### Summary

@@

### Installation
The `ppmData` package can be installed using `devtools` or `remotes` R packages.

```{r,eval=FALSE}
install.packages('devtools')
devtools::install_github('skiptoniam/ppmData')
```

### Example

Here is an example using a dataset from the `ppmData` package. We setup a quadrature scheme for the species \textit{Tasmaphena sinclairi} located within Tasmania, Australia.

```{r, message=FALSE}
library(ppmData)
path <- system.file("extdata", package = "ppmData")
lst <- list.files(path=path, pattern='*.tif',full.names = TRUE)
preds <- rast(lst)
presences <- subset(snails,SpeciesID %in% "Tasmaphena sinclairi")
npoints <- 1000
ppmdata1 <- ppmData(npoints = npoints, presences=presences,
                    window = preds[[1]], covariates=preds)
```

Here we plot the quadrature scheme. The red points represent the known locations of \textit{Tasmaphena sinclairi}. The black points represent the quadrature locations. Quasi-random quadrature where the integration points are generated using a quasi-random areal sample.
```{r fig1, fig.width=7, fig.height=4, fig.align='center', echo=TRUE}
plot(ppmdata1)
```
## Code of Conduct

Please note that the ppmData project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
